% !TeX root = ../../thesis.tex
\chapter*{Publications}\label{ch:publications}

% Set spacing between sentences to exaclty one space instead of Latex’s ``rubber spacing''
\frenchspacing

\section*{Journal papers}

    Weltje, G.J. and \textbf{Paredis, B.}, %
    2020. %
    Geostatistical modelling of compositional variability across granitoid complexes: Its relevance to petrogenetic interpretations and specification of parent-rock properties in sediment-generation models. %
    Earth-Science Reviews 208, %
    pp. xx-xx %

    \textbf{Paredis, B.}, Weltje, G.J., Heins, W.A., %
    2020. %
    Quantitative analysis of the joint variability of rock texture and composition in thin section: The Generalized Griffiths Descriptor and its application to sediment generation from granitoids. %
    Earth-Science Reviews 205, %
    pp. xx-xx %

    Weltje, G.J., \textbf{Paredis, B.}, Caracciolo, L., Heins, W.A., %
    2018. %
    Quantitative analysis of crystal-interface frequencies in granitoids: Implications for modelling of parent-rock texture and its influence on the properties of plutoniclastic sands. %
    Sedimentary Geology 375, %
    pp. 72-85 %


\section*{Conference proceedings and abstracts}

    \textbf{Paredis, B.} and Weltje, G.J., %
    2018. %
    Numerical modelling of sediment generation: characterizing parent rock’s properties by digital petrography. %
    Oral presentation at the 6\textsuperscript{th} International Geologica Belgica Meeting. %
    September 12-14, 2018. %
    Leuven, Belgium. %

    \textbf{Paredis, B.} and Weltje, G.J., %
    2018. %
    Numerical modelling of sediment generation: characterization of parent rock properties. %
    Oral presentation at 20\textsuperscript{th} International Sedimentological Congress. %
    August 12-17, 2018. %
    Québec, Canada. %

    \textbf{Paredis, B.} and Weltje, G.J., %
    2018. %
    Numerical modelling of sediment generation: characterisation of granitoid parent rocks. %
    Oral presentation at 4\textsuperscript{th} meeting of the Working Group on Sediment Generation (WGSG). %
    June 27-29, 2018. %
    Dublin, Ireland. %

    \textbf{Paredis, B.} and Weltje, G.J., %
    2017. %
    Numerical modelling of sediment generation: a modular approach. %
    Oral presentation at the 33\textsuperscript{rd} International Meeting of Sedimentology. %
    October 10-12, 2017. %
    Toulouse, France. %

    \textbf{Paredis, B.} and Weltje, G.J., %
    2016. %
    Numerical modelling of sediment generation. %
    Poster presentation at 3\textsuperscript{rd} meeting of the Working Group on Sediment Generation (WGSG). %
    July 4-6, 2016. %
    Leuven, Belgium. %


\section*{Miscellaneous}

\nonfrenchspacing


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Keep the following \cleardoublepage at the end of this file,
% otherwise \includeonly includes empty pages.
\cleardoublepage

% vim: tw=70 nocindent expandtab foldmethod=marker foldmarker={{{}{,}{}}}
